### 2021-08-01 paper.tex
made changes to position of images, and more
fixed the border not appearing in acknowledgement page
added a few subsections and subsubsections

\documentclass[11pt]{report}

@@

	% Title page
	\input{titlepage.tex}

@@

	\subsubsection{Architecture}

@@

	\textbf{Convolutional Layer}:
	In a CNN, the input is a tensor with a shape: (number of inputs) x (input
	height) x (input width) x (input channels). After passing through a
	convolutional layer, the image becomes abstracted to a feature map, also
	called an activation map, with shape: (number of inputs) x (feature map
	height) x (feature map width) x (feature map channels). A convolutional
	layer within a CNN generally has the following attributes:

@@

	\textbf{Pooling Layer}:
	Convolutional networks may include local and/or global pooling layers along
	with traditional convolutional layers. Pooling layers reduce the dimensions
	of data by combining the outputs of neuron clusters at one layer into a
	single neuron in the next layer. Local pooling combines small clusters,
	tiling sizes such as 2 x 2 are commonly used. Global pooling acts on all the
	neurons of the feature map. There are two common types of pooling in popular
	use: max and average. Max pooling uses the maximum value of each local
	cluster of neurons in the feature map, while average pooling takes the
	average value.

	\textbf{ReLU Layer}:

@@

	\textbf{Fully Connected Layer}

@@

	\textbf{Loss Layer}

@@

	\textbf{Receptive field}

@@

	\textbf{Weights}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=\linewidth]{imgs/vgg16_conf}
		\caption{VGG16 configuration}%
		\label{fig:vgg16_conf}
	\end{figure}

@@

	\begin{wrapfigure}{r}{0.5\textwidth}
		\begin{center}
			\includegraphics[ width=0.5\textwidth ]{imgs/resnet_arch2.png}
		\end{center}
		\caption{Resnet Architecture}
	\end{wrapfigure}

@@

@@

@@

	\textbf{Plain Network}

@@

	\textbf{Residual Network}
	Based on the above plain network, we insert shortcut connections which turn
	the network into its counterpart residual version. The identity shortcuts
	can be directly used when the input and output are of the same dimensions.
	When the dimensions increase, we consider two options:
	\begin{enumerate}
		\item The shortcut still performs identity mapping, with extra zero
			entries padded for increasing dimensions. This option introduces no
			extra parameter
		\item The projection shortcut is used to match dimensions (done by 1×1
			convolutions).
	\end{enumerate}
	For both options, when the shortcuts go across feature maps of two sizes,
	they are performed with a stride of 2 \cite[4]{he2015deep} .

	\begin{figure}[h]
		\centering
		\includegraphics[width=\linewidth]{imgs/resnet_arch.png}
		\caption{resnet50 configuration}%
		\label{fig:resnet conf}
	\end{figure}

>>>>

\documentclass[10pt]{report}

@@

	\pagenumbering{roman}
	% Title page
	\input{titlepage.tex}

@@

	\subsection{Architecture}

@@

	\subsection{Convolutional Layer}:

	In a CNN, the input is a tensor with a shape: (number of inputs) x (input
	height) x (input width) x (input channels). After passing through a
	convolutional layer, the image becomes abstracted to a feature map, also
	called an activation map, with shape: (number of inputs) x (feature map
	height) x (feature map width) x (feature map channels). A convolutional
	layer within a CNN generally has the following attributes:

@@

	\subsection{Pooling Layer}:

	Convolutional networks may include local and/or global pooling layers along
	with traditional convolutional layers. Pooling layers reduce the dimensions
	of data by combining the outputs of neuron clusters at one layer into a
	single neuron in the next layer. Local pooling combines small clusters,
	tiling sizes such as 2 x 2 are commonly used. Global pooling acts on all the
	neurons of the feature map. There are two common types of pooling in popular
	use: max and average. Max pooling uses the maximum value of each local
	cluster of neurons in the feature map, while average pooling takes the
	average value.

	\subsection{ReLU Layer}:

@@

	\subsection{Fully Connected Layer}

@@

	\subsection{Loss Layer}

@@

	\subsection{Receptive field}

@@

	\subsection{Weights}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.5\linewidth]{imgs/vgg16_conf}
		\caption{VGG16 configuration}%
		\label{fig:vgg16_conf}
	\end{figure}

@@

@@

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\linewidth]{imgs/resnet_arch.png}
		\caption{resnet50 configuration}%
		\label{fig:resnet conf}
	\end{figure}

@@

	\begin{wrapfigure}{r}{0.5\textwidth}
		\begin{center}
			\includegraphics[ width=0.45\textwidth ]{imgs/resnet_arch2.png}
		\end{center}
		\caption{Resnet Architecture}
	\end{wrapfigure}

@@

	\subsubsection{Plain Network}

@@

	\subsubsection{Residual Network}

	Based on the above plain network, we insert shortcut connections which turn
	the network into its counterpart residual version. The identity shortcuts
	can be directly used when the input and output are of the same dimensions.
	When the dimensions increase, we consider two options:
	\begin{enumerate}
		\item The shortcut still performs identity mapping, with extra zero
			entries padded for increasing dimensions. This option introduces no
			extra parameter
		\item The projection shortcut is used to match dimensions (done by 1×1
			convolutions).
	\end{enumerate}
	For both options, when the shortcuts go across feature maps of two sizes,
	they are performed with a stride of 2 \cite[4]{he2015deep} .
